---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# leaflet.providers

<!-- badges: start -->

[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/leslie-huang/leaflet.providers?branch=master&svg=true)](https://ci.appveyor.com/project/leslie-huang/leaflet.providers)
[![Travis build status](https://travis-ci.org/leslie-huang/leaflet.providers.svg?branch=master)](https://travis-ci.org/leslie-huang/leaflet.providers)
[![Codecov test coverage](https://codecov.io/gh/leslie-huang/leaflet.providers/branch/master/graph/badge.svg)](https://codecov.io/gh/leslie-huang/leaflet.providers?branch=master)

<!-- badges: end -->

The goal of leaflet.providers is to provide regularly updated data on the third-party tile providers supported by `leaflet`. This package is to be used with `leaflet`.

## Installation

You can install the released version of `leaflet.providers` from [CRAN](https://CRAN.R-project.org):

``` {r craninstall, eval = FALSE}
# CRAN version
install.packages("leaflet.providers")
```

And the development version from [GitHub](https://github.com/) with:

``` {r devtoolsinstall, eval = FALSE}
# install.packages("devtools")
devtools::install_github("leslie-huang/leaflet.providers")
```

## Example

This is a basic example of the data that is automatically loaded with `leaflet.providers`.

### View Leaflet.js version number from which the data is derived

```{r example0}
library(leaflet.providers)
providers_data <- providers()

providers_data$version_num
```

### View supported tile providers

```{r example}
str(providers_data$providers)

```

### View snippet of providers.details

```{r example2}
str(providers_data$providers_details, vec.len = 1, list.len=3)
```
