---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[leaflet]: https://rstudio.github.io/leaflet/

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# leaflet.providers

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/leaflet.providers)](https://CRAN.R-project.org/package=leaflet.providers)
[![R-CMD-check](https://github.com/rstudio/leaflet.providers/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/rstudio/leaflet.providers/actions)
[![Codecov test coverage](https://codecov.io/gh/rstudio/leaflet.providers/branch/main/graph/badge.svg)](https://app.codecov.io/gh/rstudio/leaflet.providers?branch=main)

<!-- badges: end -->

The goal of `leaflet.providers` is to provide regularly updated data on the third-party tile providers supported by `leaflet`. The data is extracted from [leaflet-providers.js](https://github.com/leaflet-extras/leaflet-providers).

While `leaflet.providers` will be regularly released with updated providers data, the package comes with functions `use_providers()` and `get_providers()`, which enable users to fetch up-to-date providers information directly from [leaflet-providers.js](https://github.com/leaflet-extras/leaflet-providers) between package updates and to load this providers data in `leaflet`. Users may also fetch older versions of the providers data with the `leaflet-providers.js` version number.

## Installation

You can install the released version of `leaflet.providers` from [CRAN](https://CRAN.R-project.org):

``` {r craninstall, eval = FALSE}
# CRAN version
install.packages("leaflet.providers")
```

And the development version from [GitHub](https://github.com/) with:

``` {r pakinstall, eval = FALSE}
pak::pak("rstudio/leaflet.providers")
```

## Example

The following are basic example of the default providers data that comes `leaflet.providers` as well as the available methods to fetch and load custom providers.

### Usage

In general, you do not need to load or interact with `leaflet.providers` directly.
Instead, `leaflet.providers` is used indirectly by the [leaflet package][leaflet] in the `leaflet::addProviderTiles()` function.

``` r
library(leaflet)

leaflet()  |>
  setView(lng = -71.0589, lat = 42.3601, zoom = 12) |>
  addTiles() |>
  addProviderTiles("OpenTopoMap")
```

### Fetch custom providers

You can choose a specific version of `leaflet-providers.js` by calling `use_providers()` with the desired version or the providers from a desired version:

``` r
# Shorthand method:
use_providers("1.7.0")

# Longer method:
# 1. Retrieve v 1.7.0
providers_170 <- get_providers("1.7.0")

# 2. Load custom providers data
use_providers(providers_170)

# Reset loaded providers to default providers
use_providers()
```

Now that `use_providers()` has been called with a custom
`leaflet.providers` object obtained via `get_providers()` (in this case,
a previous version of the data),
[`leaflet`][leaflet] will use the custom
providers instead of the default provider data.

> Note that the package `V8` is required for `get_providers()`.

### Default providers

```{r providersdefault, eval = FALSE}
library(leaflet.providers)

str(providers_default(), max.level = 2)
```

<div style = "height:150px; overflow-y: scroll;">

```{r providersdefault1, echo = FALSE}
library(leaflet.providers)

str(providers_default(), max.level = 2)
```

</div>

### View the loaded providers data

#### The version number of the source leaflet-providers.js

```{r example0}
providers_loaded()$version_num
```

#### Supported tile providers

```{r examplept1, eval = FALSE}
names(providers_loaded()$providers)
```

<div style = "height:150px; overflow-y: scroll;">

```{r examplept2, echo=FALSE}
names(providers_loaded()$providers)
```

</div>

#### Tile providers' details

```{r example2pt1, eval = FALSE}
str(providers_loaded()$providers_details)
```

<div style = "height:150px; overflow-y: scroll;">

```{r example2pt2, echo=FALSE}
str(providers_loaded()$providers_details, list.len = 200)
```

</div>
