---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# leaflet.providers

<!-- badges: start -->

[![Build status](https://ci.appveyor.com/api/projects/status/jn298w6o6pf8mpx1?svg=true)](https://ci.appveyor.com/project/leslie-huang/leaflet-providers)
[![Travis build status](https://travis-ci.org/leslie-huang/leaflet.providers.svg?branch=master)](https://travis-ci.org/leslie-huang/leaflet.providers)
[![Codecov test coverage](https://codecov.io/gh/leslie-huang/leaflet.providers/branch/master/graph/badge.svg)](https://codecov.io/gh/leslie-huang/leaflet.providers?branch=master)

<!-- badges: end -->

The goal of leaflet.providers is to provide regularly updated data on the third-party tile providers supported by `leaflet`. The data is extracted from [leaflet-providers.js](https://github.com/leaflet-extras/leaflet-providers). This package is to be used with `leaflet`. 

Using `use_providers()` and `get_providers`, users may fetch up-to-date providers information to be used in `leaflet`.

## Installation

You can install the released version of `leaflet.providers` from [CRAN](https://CRAN.R-project.org):

``` {r craninstall, eval = FALSE}
# CRAN version
install.packages("leaflet.providers")
```

And the development version from [GitHub](https://github.com/) with:

``` {r devtoolsinstall, eval = FALSE}
# install.packages("devtools")
devtools::install_github("leslie-huang/leaflet.providers")
```

## Example

This is a basic example of the data that is automatically loaded with `leaflet.providers` and the available methods.

### Use up-to-date providers and providers' details

```{r get_providers_ex}
library(leaflet.providers)

todays_providers <- get_providers()

# Set custom providers and providers' details

use_providers(todays_providers)
```

Now that `use_providers` has been called with today's providers, [`leaflet`](http://rstudio.github.io/leaflet) will use the latest providers data.

### View Leaflet.js version number from which the data is derived

```{r example0}
providers_data <- providers()

providers_data$version_num
```

### View supported tile providers

```{r examplept1, eval = FALSE}
str(providers_data$providers)
```

<div style = "height:150px; overflow-y: scroll;">

```{r examplept2, echo=FALSE}
str(providers_data$providers, list.len = 200)
```

</div>

### View snippet of tile providers' details


```{r example2pt1, eval = FALSE}
str(providers_data$providers_details)
```

<div style = "height:150px; overflow-y: scroll;">

```{r example2pt2, echo=FALSE}
str(providers_data$providers_details, list.len = 200)
```

</div>
